This is the title [Article v\versionnumber]

### 2022-08-25 manuscript/manuscript.tex
Continue the rework of the Tutorial part. Still unfinished.

@@

\begin{equation}
	S_{k}^\textit{trans} = -R \left( \gamma + \frac{1}{N_\textit{k}} \sum _{i=1}^{N_k} \ln g_{NN, \textit{i}}(\textbf{r}) \right)
\end{equation}
and
\begin{equation}

	S_{k}^\textit{orient} = -R \left( \gamma + \frac{1}{N_k} \sum _{i=1}^{N_k} \ln g_{NN, i}(\omega) \right)
	,

\end{equation}
where $N_\textit{k}$ is the number of water molecules found in voxel k, $\gamma$ is Euler's constant that accounts for the bias in naive entropy estimator, and $g_\textit{NN}$ is the nearest neighbor estimate.

@@

\begin{equation}

	S_\textit{k} = -R \left( \gamma + \frac{1}{N_\textit{k}} \sum _{i=1}^{N_k} \ln g_{NN, \textit{i}}(\textbf{r},\omega) \right)

\end{equation}

@@

Run the MD using \software{pmemd.cuda}:
\begin{lstlisting}
pmemd.cuda \
	-O \
	-i 100ns-npt-restraint.in \
	-o md-01.out \
	-p solvated.parm7 \
	-c EQUIL-DONE.rst \
	-x md-01.nc \
	-r md-01.ncrst \
	-ref EQUIL-DONE.rst
\end{lstlisting}
\subsection{Running the GIST analysis}
\todo{GIST analysis can be divided in three steps.
\cite{Ramsey2016}}

\todo{Step 1: Identify and define the region of interest
In order to run a GIST analysis, the region where the solvent properties will be calculated must be first defined. This region is represented by a rectangular prism centered at (x,y,z) with a dimension of $L_x x L_y x L_z$. This region is further subdivided into three-dimesional grids based on the spacing that's specified. A smaller spacing indicates a higher resolution grids, but in return will slow down the calculation.  A default value of 0.5 A is used that provides reasonable accuracy and speed of the calculation.  }

\todo{In ccptraj, the rectangular prism is defined by the command:}

\todo {gist gridcntr <xcoordinate>  <ycordinated> <zcoordinate> griddim <xval> <yval> <zval> gridspacn <val>
}

\todo{The center of the grid is defined by gridcntr, the dimensions of the grid is defined by griddim, and the spacing is defined by gridspacn.}

\todo{The region can be defined using a ligand in a specific binding pocket of the protein, a specific residue of the protein, or the whole protein itself. A helper script FindCentroid.py can be used to determine the centroid of the region of interest as well as the dimensions of the rectangular prism that will fully enclose the region. A pdb file is needed as an input and the rectangular prism will be centered based on the centroid of the given structure.}

\todo {python FindCentroid.py -i structure.pdb  }

\todo{Step 2: Run GIST using cpptraj}
\todo{GIST is incorporated in cpptraj which requires the topology and the trajectory of the MD simulation to be analayzed. The commands needed to run GIST in cpptraj can be written in an input file (e.g gist.in) for convenience. The basic comands are:}

@@

\todo{cpptraj -i gist.in}

\todo{Aside from the commands defining the region of interest, there are other options available to specify the GIST analysis. Here is the full list that can be added to the third line of the input file:} 
\begin{itemize}
	\item{[doorder] Calculate the water order parameter [reference] for each voxel.}
	\item{[doeij] Calculate the triangular matrix representing the water-water interactions between pairs of voxels (see below).}
	\item{[skipE] Skip all energy calculations (cannot be specified with ’doeij’).}
	\item{[skipS Skip all the entropy calculations.]}
	\item{[refdens rdval>] Reference density of bulk water, used in computing $g_O, g_H$, and the translational entropy. Default is 0.0334 molecules/Å3.}
	\item{[temp <tval>] Temperature of the input trajectory.}
	\item{[noimage] Disable distance imaging in energy calculation.}
	\item{[gridcntr <xval> <yval> <zval>] Coordinates (Å) of the center of the grid (default 0.0, 0.0, 0.0).}
	\item{[griddim <xval> <yval> <zval>] Grid dimensions along each coordinate axis (default 40, 40, 40).}
	\item{[gridspacn <spaceval>] Grid spacing (linear dimension of each voxel) in Angstroms. Values greater than 0.75 Å are not recommended (default 0.5 Å).}
	\item{[prefix <filename prefix>] Output file name prefix (default “gist”).}
	\item{[ext <grid extension>] Output grid file name extension (default “.dx”).}
	\item{[out <output>] Name of the main GIST output file. If not specified set to ’<prefix>-output.dat’.}
	\item{[info <info>] Name of main GIST info file. If not specified info is written to standard output.}

\end{itemize}

\todo{Step 3: Postprocessing and Analyzing GIST results}
\todo{Cppraj outputs the quantities calculated in a data explorer "DX" file format which can be easily visualized in Pymol or VMD.  Aside from the thermodynamic quantities, GIST also calculates the number densitiies of hydrogen and oxygen in each voxel. Here is a full list of quantities calculated by GIST:}

>>>>

% TODO: delete for final build
\usepackage{pdfcomment}

@@

\begin{equation}
	S_{k}^\textit{trans} = -R \left( \gamma + \frac{1}{N_\textit{k}} \sum _{i=1}^{N_k} \ln g_{NN, \textit{i}}(\textbf{r}) \right)
\end{equation}
and
\begin{equation}
	S_{k}^\textit{orient} = -R \left( \gamma + \frac{1}{N_k} \sum _{i=1}^{N_k} \ln g_{NN, i}(\omega) \right)
	,
\end{equation}
where $N_\textit{k}$ is the number of water molecules found in voxel k, $\gamma$ is Euler's constant that accounts for the bias in naive entropy estimator, and $g_\textit{NN}$ is the nearest neighbor estimate.

@@

\begin{equation}
	S_\textit{k} = -R \left( \gamma + \frac{1}{N_\textit{k}} \sum _{i=1}^{N_k} \ln g_{NN, \textit{i}}(\textbf{r},\omega) \right)
\end{equation}

@@

Run the MD using \software{pmemd.cuda}:
\begin{lstlisting}
pmemd.cuda \
	-O \
	-i 100ns-npt-restraint.in \
	-o md-01.out \
	-p solvated.parm7 \
	-c EQUIL-DONE.rst \
	-x md-01.nc \
	-r md-01.ncrst \
	-ref EQUIL-DONE.rst
\end{lstlisting}

\subsection{Running the GIST analysis}
GIST analysis can be divided in three steps: defining a region of interest, running GIST using \software{cpptraj}, and post-processing and analysis.
\cite{Ramsey2016}

\paragraph{Identify and define the region of interest}
In order to run a GIST analysis, the region where the solvent properties will be calculated must be first defined. This region is represented by a rectangular prism centered at (x, y, z) with $N_x \times N_y \times N_z$ voxels, where each voxel is cubic with a sidelength of \inlinecode{gridspacn}.
While integrals over GIST quantities are independent of the voxel size, individual voxel values converge slower at high resolutions.\pdfcomment{The calculation actually can actually get faster at higher resolution, because the same grid is used in the nearest-neighbor search.}
A default value of 0.5 A is used that provides reasonable discretization for many use-cases.

In \software{ccptraj}, the rectangular prism is defined by parameters of the \inlinecode{gist} command.
The center of the grid is defined by \inlinecode{gridcntr}, the dimensions of the grid is defined by \inlinecode{griddim}, and the spacing is defined by \inlinecode{gridspacn}.

\begin{lstlisting}
gist gridcntr <x> <y> <z> \
     griddim <Nx> <Ny> <Nz> gridspacn <val>
\end{lstlisting}

The region can be defined using a ligand in a specific binding pocket of the protein, a specific residue of the protein, or the whole protein itself. A helper script FindCentroid.py \todo{(upload FindCentroid.py!)} can be used to determine the centroid of the region of interest as well as the dimensions of the rectangular prism that will fully enclose the region. A pdb file is needed as an input and the rectangular prism will be centered based on the centroid of the given structure.

\begin{lstlisting}
python FindCentroid.py -i structure.pdb
\end{lstlisting}

\paragraph{Run GIST using cpptraj}
\todo{GIST is incorporated in cpptraj which requires the topology and the trajectory of the MD simulation to be analayzed. The commands needed to run GIST in cpptraj can be written in an input file (e.g gist.in) for convenience. The basic comands are:}

@@

\begin{lstlisting}
cpptraj -i gist.in
\end{lstlisting}

\pdfcomment{Franz: I removed the list because it is very long and not complete. We can add it to the lists at the end, but then it should be complete.}
%\todo{Aside from the commands defining the region of interest, there are other options available to specify the GIST analysis. Here is the full list that can be added to the third line of the input file:} 
%\begin{itemize}
%	\item{[doorder] Calculate the water order parameter [reference] for each voxel.}
%	\item{[doeij] Calculate the triangular matrix representing the water-water interactions between pairs of voxels (see below).}
%	\item{[skipE] Skip all energy calculations (cannot be specified with ’doeij’).}
%	\item{[skipS Skip all the entropy calculations.]}
%	\item{[refdens rdval>] Reference density of bulk water, used in computing $g_O, g_H$, and the translational entropy. Default is 0.0334 molecules/Å3.}
%	\item{[temp <tval>] Temperature of the input trajectory.}
%	\item{[noimage] Disable distance imaging in energy calculation.}
%	\item{[gridcntr <xval> <yval> <zval>] Coordinates (Å) of the center of the grid (default 0.0, 0.0, 0.0).}
%	\item{[griddim <xval> <yval> <zval>] Grid dimensions along each coordinate axis (default 40, 40, 40).}
%	\item{[gridspacn <spaceval>] Grid spacing (linear dimension of each voxel) in Angstroms. Values greater than 0.75 Å are not recommended (default 0.5 Å).}
%	\item{[prefix <filename prefix>] Output file name prefix (default “gist”).}
%	\item{[ext <grid extension>] Output grid file name extension (default “.dx”).}
%	\item{[out <output>] Name of the main GIST output file. If not specified set to ’<prefix>-output.dat’.}
%	\item{[info <info>] Name of main GIST info file. If not specified info is written to standard output.}
%\end{itemize}

\paragraph{Postprocessing and Analyzing GIST results}
Cppraj outputs the quantities calculated in a data explorer "DX" file format which can be easily visualized in Pymol or VMD.
Aside from the thermodynamic quantities, GIST also calculates the number densitiies of hydrogen and oxygen in each voxel. Here is a full list of quantities calculated by GIST \todo{This is incomplete!}:
